A Tutorial on Tailored Simulation-Based Sample Size Planning for Experimental Designs with Generalized Linear Mixed Models

### 2024-11-05 _tex/manuscript.tex
Built site for gh-pages

\begin{tcolorbox}[enhanced jigsaw, opacitybacktitle=0.6, bottomrule=.15mm, bottomtitle=1mm, opacityback=0, colbacktitle=quarto-callout-important-color!10!white, coltitle=black, left=2mm, colback=white, breakable, toptitle=1mm, titlerule=0mm, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{Important}, arc=.35mm, rightrule=.15mm, toprule=.15mm, leftrule=.75mm, colframe=quarto-callout-important-color-frame]

>>>>

\begin{tcolorbox}[enhanced jigsaw, leftrule=.75mm, coltitle=black, opacityback=0, breakable, toptitle=1mm, colbacktitle=quarto-callout-important-color!10!white, toprule=.15mm, arc=.35mm, colback=white, bottomrule=.15mm, left=2mm, colframe=quarto-callout-important-color-frame, rightrule=.15mm, opacitybacktitle=0.6, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{Important}, bottomtitle=1mm, titlerule=0mm]
